%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Tushar Dadlani} % Your name

\address{(650)~$\cdot$~318~$\cdot$~1695 \\ tushardadlani@cmu.edu\\ } % Your phone number and email

\address{333, Escuela Avenue \\ Mountain View, CA, 94040} % Your address


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Carnegie Mellon University} \hfill {\em August 2013-December 2014(expected)} \\ 
MS in Software Engineering\\
Overall GPA: 4.0/4.0\\


{\bf Manipal University} \hfill {\em August 2007-July 2011} \\ 
BE Computer Science and Engineering\\
Overall GPA: 7.67/10
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python , C, C++, Java, Bash scripting, Ruby, MATLAB \\
Tools & Vim, SVN, Git, Mercurial.\\
Other technologies & Virtualization, Openindiana, ZFS, Android.
\end{tabular}

\underline{\bf Research:} Detection of privacy concerns in the modern smart phone by applying machine learning to smart phone sensor data.
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Carnegie Mellon University}{August 2013 - Present}{Graduate Research Assitant}{Mountain View, CA}
\item Detection and prevention of LTE network DDoS attacks. Simulated using NS3.
\item{\underline{Technologies used:} C, C++, NS3.}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Coriolis Technologies}{July 2011 - June 2013}{Member of Technical Staff}{Pune, MH, India}
\item Automated customization of Openindiana installation discs from source code.
\item Secured remote server logs used for debugging at customer support site.
\item Ported an existing KVM based virtualization solution to run on Xen.
\item Helped in protoyping a remote desktop infrastructure solution using iSCSI protocol and QCOW2 disk.
\item{\underline{Technologies used:} Bash Scripting, Python, C.	}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{EMC Corporation (RSA)}{January 2011 - June 2011}{College Intern}{Bangalore, KA, India}
\item Created an Android application to establish federatated identity on mobile platform.
\item Created a Jabber based Chat Bot that would study attacker mindset.
\item{\underline{Technologies used:} Python, Jabber, Android.}
\end{rSubsection}

\end{rSection}



\begin{rSection}{Other experience}

\item{Website administrator for TEDxManipal 2010.}
\item{Coordinated campus recruitment for 1500 students. (2010-2011)}
\item{Teach for India campus amabassador (2010-2011)}
\item{Code for India volunteer on defining the specifications for the tech-enabled learning ecosystem. }

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}